---
title: "Developing Data Products"
subtitle:  "week 3 assignment"
author: |
    | Cheng-Han Yu, Applied Math and Statistics, UC Santa Cruz
date: "`r Sys.Date()`"
output: 
  ioslides_presentation:
    incremental: yes
    logo: soelogo.jpg
    footer: no
    widescreen: yes
    transition: default
    css: ioslides_style.css
    fig_width: 5
    fig_height: 3
    fig_caption: true
    mathjax: "default"
    keep_md: no
---

## Assignment instructions

- Create a **web page presentation** using R Markdown that features a plot created with **Plotly**.
- Host your webpage on either [GitHub](https://github.com) Pages, [RPubs](https://rpubs.com/), or [NeoCities](https://neocities.org/).
- Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly.

## Scatter plot Shots v.s. Time for each Position of worldcup dataset
```{r wroldcup, echo = TRUE, eval=TRUE, include=TRUE,message=FALSE, warning=FALSE}
library(faraway) 
library(plotly)
data(worldcup)
worldcup_scatter <- worldcup %>%
  ggplot(aes(x = Time, y = Shots, color = Position)) +
  geom_point()
```


## Slide with Plot

```{r plotly, echo=TRUE, message=FALSE, warning=FALSE, fig.height=5,fig.align='center', fig.width=10}
ggplotly(worldcup_scatter)
```

